Towards Proof-Reconstruction of Problems in Classical Propositional Logic

### 2017-09-11 paper/sections/preliminaries.tex
[ paper ] implementation added, some proofs added.

\textit{Propositions.}
We define the classical propositional logic as usual.
A proposition is an expression of indivisible propositional atoms
(e.g., symbols $φ₀, φ₁, \cdots$),
binary logic connectives ($∧, ∨, ⇒, ⇔)$,
propositional negation $(\neg)$, and logic constants $\bot$
and $\top$. We use the inductive definition of the set \PROP
defined in \cite{VanDalen1994} as the mechanism to produce any
propositional formula.
Then, $ϕ_i \in \PROP$ for all $i \in \mathbb{N}$.
If $(\phi\ \square\ \psi)$ stands for a proposition that use a
binary connective where is the symbol $\square$; when $\phi, \psi\in
\PROP$, then $(\phi\ \square\ \psi) \in \PROP$.
If $\phi \in \PROP$, then $(\neg \phi) \in \PROP$.
Finally, $\bot, \top \in \PROP$.

\emph{Derivations.}
A derivation of $φ$ is a mechanism to obtain the conclusion φ from
the application of some deduction steps. Such a deduction step has
the form of a set of propositional \emph{premises} that conclude the
result: one or more propositions. As we show in the following
figure, the premises are always above the line, and the conclusions
are below it. As a notation convention, if the name of a rule used
in the derivation step is typed using verbatim, that means, it is
available in our implementation for the CPL (see the syntax module in
\cite{AgdaProp}) used in the proof reconstruction latter.

@@

\emph{Theorems.}
A sequent $Γ ⊢ φ$ represents a theorem, but we
define it as a relation between a set of propositions premises $Γ$,
and $φ$ as the sequent's conclusion.
The symbol $⊢$ is called turnstile.
If $Γ = ∅$, we write $⊢ φ$, and we say that $φ$ is a theorem
Then, a theorem, $Γ ⊢ φ$ , means that there is a derivation with
conclusion $φ$ and with all (uncancelled) hypotheses in $Γ$.

@@

\[
\label{eq:PEM-RAA}
\begin{bprooftree}
\AxiomC{}
\RightLabel{\scriptsize\tt PEM}
\UnaryInfC{Γ ⊢ φ ∨ ¬ φ}
\end{bprooftree}\qquad
\begin{bprooftree}
\AxiomC{Γ, ¬ φ ⊢ ⊥}
\RightLabel{\scriptsize\tt RAA}
\UnaryInfC{Γ ⊢ φ}
\end{bprooftree}
\]

@@

\begin{figure}
\[%\scalebox{0.9}{
\begin{bprooftree}
\AxiomC{}
\RightLabel{\scriptsize\tt assume $\varphi$}
\UnaryInfC{$\Gamma , \varphi \vdash \varphi$}
\end{bprooftree}\quad
\begin{bprooftree}
\AxiomC{$\Gamma \vdash \varphi$}
\RightLabel{\scriptsize\tt weaken $\psi$}
\UnaryInfC{$\Gamma , \psi \vdash \varphi$}
\end{bprooftree}\quad
\begin{bprooftree}
\AxiomC{}
\RightLabel{\scriptsize\tt $\top$-intro}
\UnaryInfC{$\Gamma \vdash \top$}
\end{bprooftree}\quad
\begin{bprooftree}
\AxiomC{$\Gamma \vdash \bot$}
\RightLabel{\scriptsize\tt $\bot$-elim $\varphi$}
\UnaryInfC{$\Gamma \vdash \varphi$}
\end{bprooftree}
%}
\]

\[%\scalebox{0.9}{
\begin{bprooftree}
\AxiomC{$\Gamma , \varphi \vdash \bot$}
\RightLabel{\scriptsize\tt $\neg$-intro}
\UnaryInfC{$\Gamma \vdash \neg \varphi$}
\end{bprooftree}\quad
\begin{bprooftree}
\AxiomC{$\Gamma \vdash \neg \varphi$}
\AxiomC{$\Gamma \vdash \varphi$}
\RightLabel{\scriptsize\tt $\neg$-elim}
\BinaryInfC{$\Gamma \vdash \bot$}
\end{bprooftree}\quad
\begin{bprooftree}
\AxiomC{$\Gamma \vdash \varphi$}
\AxiomC{$\Gamma \vdash \psi$}
\RightLabel{\scriptsize\tt $\wedge$-intro}
\BinaryInfC{$\Gamma \vdash \varphi \wedge \psi$}
\end{bprooftree}
%}
\]

\[%\scalebox{0.9}{
\begin{bprooftree}
\AxiomC{$\Gamma \vdash \varphi \wedge \psi$}
\RightLabel{\scriptsize\tt $\wedge$-proj$_1$}
\UnaryInfC{$\Gamma\vdash \varphi$}
\end{bprooftree}\quad
\begin{bprooftree}
\AxiomC{$\Gamma \vdash \varphi \wedge \psi$}
\RightLabel{\scriptsize\tt $\wedge$-proj$_2$}
\UnaryInfC{$\Gamma\vdash \psi$}
\end{bprooftree}\quad
\begin{bprooftree}
\AxiomC{$\Gamma \vdash \varphi$}
\RightLabel{\scriptsize\tt $\vee$-intro$_1$ $\psi$}
\UnaryInfC{$\Gamma \vdash \varphi \vee \psi$}
\end{bprooftree}
%}
\]

\[%\scalebox{0.9}{
\begin{bprooftree}
\AxiomC{$\Gamma \vdash \psi$}
\RightLabel{\scriptsize\tt $\vee$-intro$_2$ $\varphi$}
\UnaryInfC{$\Gamma \vdash \varphi \vee \psi$}
\end{bprooftree}\quad
\begin{bprooftree}
\AxiomC{$\Gamma ,\varphi \vdash \gamma $}
\AxiomC{$\Gamma , \psi  \vdash \gamma$}
\RightLabel{\scriptsize\tt $\vee$-elim}
\BinaryInfC{$\Gamma , \varphi \vee \psi \vdash \gamma$}
\end{bprooftree}\quad
\begin{bprooftree}
\AxiomC{$\Gamma , \varphi \vdash \psi$}
\RightLabel{\scriptsize\tt $\Rightarrow$-intro}
\UnaryInfC{$\Gamma \vdash \varphi \Rightarrow \psi$}
\end{bprooftree}
%}
\]

\[
%\scalebox{0.9}{
\begin{bprooftree}
\AxiomC{$\Gamma \vdash \varphi \Rightarrow \psi$}
\AxiomC{$\Gamma \vdash \varphi$}
\RightLabel{\scriptsize\tt $\Rightarrow$-elim}
\BinaryInfC{$\Gamma \vdash \psi$}
\end{bprooftree}\quad
\begin{bprooftree}
\AxiomC{$\Gamma , \varphi \vdash \psi$}
\AxiomC{$\Gamma , \psi \vdash \varphi$}
\RightLabel{\scriptsize\tt $\Leftrightarrow$-intro}
\BinaryInfC{$\Gamma \vdash \varphi \Leftrightarrow \psi$}
\end{bprooftree}
%}
\]

\[
%\scalebox{0.9}{
\begin{bprooftree}
\AxiomC{$\Gamma \vdash \varphi$}
\AxiomC{$\Gamma \vdash \varphi \Leftrightarrow \psi$}
\RightLabel{\scriptsize\tt $\Leftrightarrow$-elim$_1$}
\BinaryInfC{$\Gamma \vdash \psi$}
\end{bprooftree}\quad
\begin{bprooftree}
\AxiomC{$\Gamma \vdash \varphi$}
\AxiomC{$\Gamma \vdash \varphi \Leftrightarrow \psi$}
\RightLabel{\scriptsize\tt $\Leftrightarrow$-elim$_2$}
\BinaryInfC{$\Gamma \vdash \psi$}
\end{bprooftree}
%}
\]

@@

\emph{Proof Trees.} We use trees to represent derivations and
natural deduction proofs. In a proof tree, the root is the
conclusion of the entire derivation. The nodes labeled with
the name of the inference rules contains the result of applying the
rule to their parents. The leaves in the tree become the premises,
not all necessary canceled (see a better discussion on cancellation
of hypotheses in \cite{VanDalen1994}).
\improvement{Include a tree of a proof tree.}
\end{document}

>>>>

\textit{Propositions.}
We define the classical propositional logic as usual.
A proposition is an expression of indivisible propositional atoms
(e.g., symbols $φ₀, φ₁, \cdots$),
binary logic connectives ($∧, ∨, ⇒, ⇔)$,
propositional negation $(¬)$, and logic constants $⊥$
and $⊤$. We use the inductive definition of the set \PROP
defined in \cite{VanDalen1994} as the mechanism to produce any
propositional formula.
Then, $ϕ_i \in \PROP$ for all $i \in \mathbb{N}$.
If $(φ\ \square\ ψ)$ stands for a proposition that use a
binary connective where is the symbol $\square$; when $φ, ψ\in
\PROP$, then $(φ\ \square\ ψ) \in \PROP$.\change{rewrite this}
If $φ \in \PROP$, then $(¬ φ) \in \PROP$.
Finally, $⊥, ⊤ \in \PROP$.

\emph{Derivations.}
A derivation of $φ$ is a mechanism to obtain the conclusion $φ$ from
the application of some deduction steps. Such a deduction step has
the form of a set of propositional \emph{premises} that conclude the
result: one or more propositions. As we show in the following
figure, the premises are always above the line, and the conclusions
are below it. As a notation convention, if the name of a rule used
in the derivation step is typed using verbatim, that means, it is
available in our implementation for the \CPL (see the syntax module 
in \cite{AgdaProp}) used in the proof reconstruction latter.

@@

\emph{Theorems.}
A sequent $Γ ⊢ φ$ represents a theorem, but we
define it as a relation between a set of propositions premises $Γ$,
and $φ$ as the sequent's conclusion.
The symbol $⊢$ is called turnstile.
If $Γ = ∅$, we write $⊢ φ$, and we say that $φ$ is a theorem.
Then, a theorem, $Γ ⊢ φ$ , means that there is a derivation with
conclusion $φ$ and with all (uncancelled) hypotheses in $Γ$.

@@

\label{eq:PEM-RAA}
\[
\begin{bprooftree}
\AxiomC{\ }
\RightLabel{\scriptsize\tt PEM}
\UnaryInfC{Γ ⊢ φ ∨ ¬ φ}
\end{bprooftree}
\qquad
\begin{bprooftree}
\AxiomC{Γ, ¬ φ ⊢ ⊥}
\RightLabel{\scriptsize\tt RAA}
\UnaryInfC{Γ ⊢ φ}
\end{bprooftree}
\qquad
\]

@@

\begin{figure}
\[%\scalebox{0.9}{
\begin{bprooftree}
\AxiomC{}
\RightLabel{\scriptsize\tt assume $φ$}
\UnaryInfC{$Γ , φ ⊢ φ$}
\end{bprooftree}\quad
\begin{bprooftree}
\AxiomC{$Γ ⊢ φ$}
\RightLabel{\scriptsize\tt weaken $ψ$}
\UnaryInfC{$Γ , ψ ⊢ φ$}
\end{bprooftree}\quad
\begin{bprooftree}
\AxiomC{}
\RightLabel{\scriptsize\tt $⊤$-intro}
\UnaryInfC{$Γ ⊢ ⊤$}
\end{bprooftree}\quad
\begin{bprooftree}
\AxiomC{$Γ ⊢ ⊥$}
\RightLabel{\scriptsize\tt $⊥$-elim $φ$}
\UnaryInfC{$Γ ⊢ φ$}
\end{bprooftree}
%}
\]

\[%\scalebox{0.9}{
\begin{bprooftree}
\AxiomC{$Γ , φ ⊢ ⊥$}
\RightLabel{\scriptsize\tt $¬$-intro}
\UnaryInfC{$Γ ⊢ ¬ φ$}
\end{bprooftree}\quad
\begin{bprooftree}
\AxiomC{$Γ ⊢ ¬ φ$}
\AxiomC{$Γ ⊢ φ$}
\RightLabel{\scriptsize\tt $¬$-elim}
\BinaryInfC{$Γ ⊢ ⊥$}
\end{bprooftree}\quad
\begin{bprooftree}
\AxiomC{$Γ ⊢ φ$}
\AxiomC{$Γ ⊢ ψ$}
\RightLabel{\scriptsize\tt $\wedge$-intro}
\BinaryInfC{$Γ ⊢ φ \wedge ψ$}
\end{bprooftree}
%}
\]

\[%\scalebox{0.9}{
\begin{bprooftree}
\AxiomC{$Γ ⊢ φ \wedge ψ$}
\RightLabel{\scriptsize\tt $\wedge$-proj$_1$}
\UnaryInfC{$Γ⊢ φ$}
\end{bprooftree}\quad
\begin{bprooftree}
\AxiomC{$Γ ⊢ φ \wedge ψ$}
\RightLabel{\scriptsize\tt $\wedge$-proj$_2$}
\UnaryInfC{$Γ⊢ ψ$}
\end{bprooftree}\quad
\begin{bprooftree}
\AxiomC{$Γ ⊢ φ$}
\RightLabel{\scriptsize\tt $\vee$-intro$_1$ $ψ$}
\UnaryInfC{$Γ ⊢ φ \vee ψ$}
\end{bprooftree}
%}
\]

\[%\scalebox{0.9}{
\begin{bprooftree}
\AxiomC{$Γ ⊢ ψ$}
\RightLabel{\scriptsize\tt $\vee$-intro$_2$ $φ$}
\UnaryInfC{$Γ ⊢ φ \vee ψ$}
\end{bprooftree}\quad
\begin{bprooftree}
\AxiomC{$Γ ,φ ⊢ \gamma $}
\AxiomC{$Γ , ψ  ⊢ \gamma$}
\RightLabel{\scriptsize\tt $\vee$-elim}
\BinaryInfC{$Γ , φ \vee ψ ⊢ \gamma$}
\end{bprooftree}\quad
\begin{bprooftree}
\AxiomC{$Γ , φ ⊢ ψ$}
\RightLabel{\scriptsize\tt $\Rightarrow$-intro}
\UnaryInfC{$Γ ⊢ φ \Rightarrow ψ$}
\end{bprooftree}
%}
\]

\[
%\scalebox{0.9}{
\begin{bprooftree}
\AxiomC{$Γ ⊢ φ \Rightarrow ψ$}
\AxiomC{$Γ ⊢ φ$}
\RightLabel{\scriptsize\tt $\Rightarrow$-elim}
\BinaryInfC{$Γ ⊢ ψ$}
\end{bprooftree}\quad
\begin{bprooftree}
\AxiomC{$Γ , φ ⊢ ψ$}
\AxiomC{$Γ , ψ ⊢ φ$}
\RightLabel{\scriptsize\tt $⇔$-intro}
\BinaryInfC{$Γ ⊢ φ ⇔ ψ$}
\end{bprooftree}
%}
\]

\[
\begin{bprooftree}
\AxiomC{$Γ ⊢ φ$}
\AxiomC{$Γ ⊢ φ ⇔ ψ$}
\RightLabel{\scriptsize\tt $⇔$-elim$_1$}
\BinaryInfC{$Γ ⊢ ψ$}
\end{bprooftree}
\qquad
\begin{bprooftree}
\AxiomC{$Γ ⊢ φ$}
\AxiomC{$Γ ⊢ φ ⇔ ψ$}
\RightLabel{\scriptsize\tt $⇔$-elim$_2$}
\BinaryInfC{$Γ ⊢ ψ$}
\end{bprooftree}
\]

@@

\emph{Proof Trees.} We use trees to represent derivations and
natural deduction proofs (see for instance, the proof tree in a
\Metis' derivation in Fig.~\ref{fig:metis-example}).
In a proof tree, the root is the conclusion of the entire 
derivation. The nodes labeled with the name of the inference rule 
contains the result of applying that rule to their parents. Lastly, 
the leaves in the tree become the premises, not all necessary 
canceled (see a better discussion on cancellation of hypotheses in
\cite{VanDalen1994}).

\end{document}

### 2017-09-11 paper/sections/proof-reconstruction.tex
[ paper ] implementation added, some proofs added.

\begin{tikzpicture}[scale=0.9]
\node[text width=2cm, align=center](problem) at (0,0)
  {1. CPL \\ Problem.};

@@

\node[below= 0.5cm of tstp, text width=2cm, align=center, inner sep=10pt]
  (athena) {5. \Haskell \\ Traslator.};

@@

% node[below] {send to}
\draw[->, thick] (problem) to
  % node[below] {\tiny encoding}
  (tptp);
\draw[->, thick] (tptp) to
  % node[below] {\tiny }
  (metis);
\draw[->, thick] (metis) to
  % node[below] {\tiny replies on}
  (tstp);
\draw[->, thick] (tstp) to
  % node[right] {\tiny parsing}
  (athena);
\draw[->, thick] (athena) to
  % node[below] {\tiny traslation}
  (agdafile);
\draw[->, thick] (agdafile) to
  % node[below] {\tiny type-checking}
  (agda);
\draw[->, thick] (agda) to (verified);
\draw[->, thick, gray] (agda) to (failure);
\end{tikzpicture}
\caption{proof-reconstruction overview.}
\label{fig:proof-reconstruction-workflow}
\end{figure}

The proof-reconstruction approach proposed here consists of a series
of steps similar to the workflow presented by Sultana in
\cite{sultana2015}. This process is a translation from a source
system to a target system. In our case, the system of origin, the
automatic theorem prover, is \Metis; the target system is the proof
assistant, \Agda. We choose \Agda, but another proof assistant with
support of type theory and features similar like \Agda is valid; our
results do not depend on the proof assistant but the support of
inductive data types, termination checking, and type-checking.

Following the diagram in Fig.
\ref{fig:proof-reconstruction-workflow}, the process can begin with
a problem in \CPL that we encode in \TPTP format to be sent as the
input of the \Metis prover.
The proof-search algorithms of \Metis in step No. 3 perform a
search for a solution; if they success, \Metis
replies a derivation in \TSTP format of the proof, else \Metis may
no stop running forever or replies the problem is counter feasible.

With such a derivation, we process it with our \Haskell translator
tool, \Athena~\cite{Athena}.
\Athena parses the \TSTP format, analyze the
derivation and generates a representation of the natural deduction
proof using a version of a tree data structure (see the properties
of this tree in subsection \ref{ssec:metis-proofs}). As a result,
\Athena generates an \Agda file with such a proof. We have included
in this file, imports for \Agda libraries that give the support for
the logic~\cite{AgdaProp}, and versions of the \Metis' inference
rules~\cite{AgdaMetis}.

@@

% \footnote{We use the \Agda standard library's implementation of the List data type.}.

\subsection{A Brief Review of Agda}
\label{ssec:agda-definition}

\Agda is an interactive system for constructing proofs and programs,
based on Martin-L\"{o}f's type theory and extended with records, parametrised
modules, among other features.
One of the main strengths of \Agda is its support for writing proofs,
which we shall call \Agda's proof engine. It consists of: support for
inductively defined types, including inductive families, and function
definitions using pattern matching on such types, normalisation during type-
checking, commands for refining proof terms, coverage checker and termination
checker.

The inductive approach for representing classical propositional logic
is better because we benefit from \Agda's proof engine and its Unicode
support that allows us writing proofs similar as we find in math text books.

In \Agda, we define a proposition formula
as an inductive type using the keyword \texttt{data}.
The \name{PropFormula} data type stands for propositions,\cite{Altenkirch2015}.
We include every connective, logic constant as a constructor.
We also define the constructor for atomic propositions \verb!Var!
to represent based on a natural number $i$, the atomic proposition
$p_i$ for a finite universe of them ($i \leq n$), this is $Fin n$ in the
definition.

\begin{verbatim}
data PropFormula : Set where
  Var : Fin n → PropFormula
  ⊤ : PropFormula
  ⊥ : PropFormula
  _∧_ _∨_ _⇒_ _⇔_ : (φ ψ : PropFormula) → PropFormula
  ¬_ : (φ : PropFormula) → PropFormula
\end{verbatim}

\begin{remark}
In the above definition, we defined all connectives, execept negation, as
a binary connective. In \Agda, we named constructors for those functions
that inhabit the data type, for example, the boolean connecetives and
the function for atomic propositions, \verb!Var!, are constructors.
The underscores in a definition like
\begin{verbatim}
_⇔_ : (φ ψ : PropFormula) → PropFormula
\end{verbatim}
stands for an argument, and \verb!(φ ψ : PropFormula)! intend for the
uncurryfied version of the type:
$$PropFormula → PropFormula → PropFormula$$
\end{remark}

@@

\subsection{Splitting the goal}

\begin{equation}
\label{eq:split-definition}
\mysplit(φ) =
\begin{cases}
\unshunt(\mysplit(φ₁)) ∧ \unshunt(φ₁ ⇒ \mysplit(φ₂)
  & φ := φ₁ ∧ φ₂\\

@@

>>>>

\begin{tikzpicture}[scale=0.9]
\node[text width=2cm, align=center](problem) at (0,0)
  {1. \CPL \\ Problem.};

@@

\node[below= 0.5cm of tstp, text width=2cm, align=center, inner sep=10pt]
  (athena) {5. \Haskell \\ Translator.};

@@

% node[below] {send to}
\draw[->, thick] (problem) to
  % node[below] {\tiny encoding}
  (tptp);
\draw[->, thick] (tptp) to
  % node[below] {\tiny }
  (metis);
\draw[->, thick] (metis) to
  % node[below] {\tiny replies on}
  (tstp);
\draw[->, thick] (tstp) to
  % node[right] {\tiny parsing}
  (athena);
\draw[->, thick] (athena) to
  % node[below] {\tiny traslation}
  (agdafile);
\draw[->, thick] (agdafile) to
  % node[below] {\tiny type-checking}
  (agda);
\draw[->, thick] (agda) to (verified);
\draw[->, thick, gray] (agda) to (failure);
\end{tikzpicture}
\caption{Proof-reconstruction overview.}
\label{fig:proof-reconstruction-workflow}
\end{figure}

The proof-reconstruction approach proposed here consists of a series
of steps similar to the workflow presented by Sultana in
\cite{sultana2015}. This process is a translation from a source
system to a target system. In our case, the system of origin, the
automatic theorem prover, is \Metis; the target system is the proof
assistant, \Agda. We choose \Agda, but another proof assistant with
support of type theory and similar features like \Agda
(see a description of \Agda in section
\ref{sec:implementation}) is valid; our results do not depend on 
the proof assistant but the support of inductive data types, 
termination checking, and type-checking.

Following the diagram in Fig.
\ref{fig:proof-reconstruction-workflow}, the process can begin with
a problem in \CPL that we encode in \TPTP format to be sent as the
input of the \Metis prover.
The proof-search algorithms of \Metis in step No. 3 intend to find 
a solution; if they success, \Metis replies a derivation in \TSTP 
format of the proof, else \Metis may no stop and running forever or 
replies the problem is counter feasible.

With such a derivation, we process it with our \Haskell translator
tool, \Athena~\cite{Athena}.
\Athena parses the \TSTP format, analyze the
derivation and generates a representation of the natural deduction
proof using a version of a tree data structure (see the properties
of this tree in subsection \ref{ssec:metis-proofs}). As a result,
\Athena generates an \Agda file with such a proof. We have included
in this file, \emph{imports} that call \Agda libraries that give 
support for the logic~\cite{AgdaProp}, and versions of the \Metis' 
inference rules~\cite{AgdaMetis}.

@@

\subsection{Recursion Theorems}

\improvement{Convention notation := for equivalence between propositions}
% \footnote{We use the \Agda standard library's implementation of the List data type.}.

@@

\subsection{Emulation \Metis' Inference Rules}

\emph{Splitting.}
We take a goal and generate subgoals that all in a conjunction
prove the goal.

\begin{theorem}[{\tt thm-$\unshunt^{*}$}] $Γ ⊢ \unshunt^{*}(φ, n)$ for $n\in \mathbb{N}$, then $Γ ⊢ φ$.
\end{theorem}
\begin{proof} Use induction on the cases defined by the result of
$\unshunt^{*}$. When $n = 0$, by definition in Eq.
\ref{eq:unshunt-structured} then $Γ ⊢ φ$.
For the first case, we prove $Γ ⊢ φ₁ ⇒ (φ₂ ⇒ φ₃)$ from
$Γ ⊢ \unshunt^{*}(φ₁ ⇒ (φ₂ ⇒ φ₃), n)$.
Because $n > 0$, using induction on the second argument and the
theorem $∧⇒$\texttt{-to-}$⇒⇒$ from \cite{AgdaProp}.

\begin{equation*}
\begin{bprooftree}
\AxiomC{$Γ ⊢ \unshunt^{*}(φ₁ ⇒ (φ₂ ⇒ φ₃), n)$}
\RightLabel{By definition}
\UnaryInfC{$Γ ⊢ \unshunt^{*}(φ₁ ⇒ (φ₂ ⇒ φ₃), n-1)$}
\RightLabel{\tt thm-$\unshunt^{*}$}
\UnaryInfC{Γ ⊢ (φ₁ ∧ φ₂) ⇒ φ₃}
\RightLabel{\tt ∧⇒-to-⇒⇒}
\UnaryInfC{Γ ⊢ φ₁ ⇒ (φ₂ ⇒ φ₃)}
\end{bprooftree}
\end{equation*}

The second case proves $Γ ⊢ φ₁ ⇒ (φ₂ ∧ φ₃)$ from
 $Γ ⊢ \unshunt^{*}(φ₁ ⇒ (φ₂ ∧ φ₃), n)$ and the
theorem $⇒∧⇒$\texttt{-to-}$⇒∧$ from \cite{AgdaProp}
\begin{equation*}
\scalebox{0.95}{
$D_1$ := \begin{bprooftree}
\AxiomC{$Γ ⊢ \unshunt^{*}(φ₁ ⇒ φ₂, n) ∧ \unshunt^{*}(φ₁ ⇒ φ₃, n)$}
\RightLabel{\tt ∧-proj₁}
\UnaryInfC{$Γ ⊢ \unshunt^{*}(φ₁ ⇒ φ₂, n)$}
\RightLabel{By definition}
\UnaryInfC{$Γ ⊢ \unshunt^{*}(φ₁ ⇒ φ₂, n-1)$}
\RightLabel{\tt thm-$\unshunt^{*}$}
\UnaryInfC{$Γ ⊢ φ₁ ⇒ φ₂$}
\end{bprooftree}
}
\end{equation*}

\begin{equation*}
D_2 :=
\begin{bprooftree}
\AxiomC{$Γ ⊢ \unshunt^{*}(φ₁ ⇒ φ₂) ∧ \unshunt^{*}(φ₁ ⇒ φ₃)$}
\RightLabel{\tt ∧-proj₂}
\UnaryInfC{$Γ ⊢ \unshunt^{*}(φ₁ ⇒ φ₃, n)$}
\RightLabel{By definition}
\UnaryInfC{$Γ ⊢ \unshunt^{*}(φ₁ ⇒ φ₃, n-1)$}
\RightLabel{\tt thm-$\unshunt^{*}$}
\UnaryInfC{$Γ ⊢ φ₁ ⇒ φ₃$}
\end{bprooftree}
\end{equation*}

\begin{equation*}
\begin{bprooftree}
\AxiomC{$D_1$}
\AxiomC{$D_2$}
\RightLabel{\tt ∧-intro}
\BinaryInfC{$Γ ⊢ (φ₁ ⇒ φ₂) ∧ (φ₁ ⇒ φ₃)$}
\RightLabel{\tt ⇒∧⇒-to-⇒∧}
\UnaryInfC{Γ ⊢ φ₁ ⇒ (φ₂ ∧ φ₃)}
\end{bprooftree}
\end{equation*}
\end{proof}

The function \mysplit performs such that strategy and it has the type
\[ \mysplit : \PROP \to \PROP
\]
\begin{equation}
\label{eq:split-definition}
\mysplit(φ) =
\begin{cases}
\unshunt(\mysplit(φ₁)) ∧ \unshunt(φ₁ ⇒ \mysplit(φ₂)
  & φ := φ₁ ∧ φ₂\\

@@

The theorem is the following.

\begin{theorem}[Splitting a Goal] $Γ ⊢ \mysplit(φ) ⇒ φ$
\end{theorem}

\begin{proof}
ss
\end{proof}

The \mysplit function returns a conjunction of the subgoal. From each
\TSTP derivation, we have information of the subgoals but no how they strictly appear in that conjunction. For that reason, with \Athena, we infer the exact order in the conjunction that coincides with the conjunction given by \mysplit.

\begin{theorem} For a list of subgoals $s_0, \cdots, s_1$ with their respective theorem $Γ ⊢ s_i$, such that $\bigwedge_i s_i ⇒ \texttt{goal}$, then $Γ ⊢ \texttt{goal}$ 
\end{theorem}
